---
title: "Feature_Engineering2 & Linear.Model"
author: "Yue Wen"
output: pdf_document
---
This RMD file is about continue performing Feature engineering and build linear model to predict independent variable.

## 1. Missing data imputation
I will summarize what I  did:

1) For tax/area related missing data, there is relationship between different tax featres, it works the same way for the area  feature. Therefore, we used  the related feature to impute the missing data by simple calculation.

2) For zip code/city, what we  did here is to use longitude/latitude to find its nearest neighbor and  use the same zip/city.

3) For the missing features that contains more then  80% NA, delete them.

4) For categorical  features that contains a lot of NA, create new level missing.

5) For total area, using library(mice) to impute.

Because it takes long to run  the imputation part,  I save the result to the csv, and we don't evaluate the code below anymore. Instead, we directly import the CSV data generated.
```{r,include=FALSE}
setwd("D:/data_camp/zillow_project")
#this csv is derived by imputation_part2.R 

train <- read.csv('train_imputed2.csv', stringsAsFactors = F)
train <- train[,!names(train) %in%c("X.1","X","trans_year")]

variable_numeric = c("area_firstfloor_finished",
                     "area_base", "area_base_living",
                     "area_garage", 
                     "area_live_finished",
                     "area_liveperi_finished",
                     "area_lot",
                     "area_patio",
                     "area_pool",
                     "area_shed",
                     "area_total_calc",
                     "area_total_finished",
                     "area_unknown",
                     "tax_building",
                     "tax_land",
                     "tax_property",
                     "tax_total",
                     "latitude",
                     "longitude")
# discrete
variable_discrete = c("num_75_bath",
                      "num_bath",
                      "num_bathroom",
                      "num_bathroom_calc",
                      "num_bedroom",
                      "num_fireplace",
                      "num_garage",
                      "num_pool",
                      "num_room",
                      "num_story",
                      "num_unit")
variable_binary = c("flag_fireplace",
                    "flag_tub",
                    "flag_spa",
                    "flag_pool_spa",
                    "flag_pool_tub",
                    "tax_delinquency")

# categorical variable
variable_nominal = c("aircon",
                     "architectural_style",
                     "county",
                     "deck",
                     "framing",
                     "heating",
                     "id_parcel",
                     "material",
                     "region_city",
                     "region_county",
                     "region_neighbor",
                     "region_zip",
                     "story",
                     "zoning_landuse",
                     "zoning_landuse_county")
variable_ordinal = c("quality")

# date
variable_date = c("tax_year",
                  "build_year",
                  "tax_delinquency_year",
                  "trans_year",
                  "trans_month",
                  "trans_day",
                  "trans_date",
                  "trans_weekday")

# others
variable_unstruct = c("zoning_property")

# don't understand
variable_unknown = c('censustractandblock',
                     'rawcensustractandblock')

# Conversion
# - convert some binary to 0, 1
# - convert to date to int
# - convert to numeric to double
# - convert to discrete to int
# - convert to categorical to character
train[train$flag_fireplace == "", "flag_fireplace"] = 0
train[train$flag_fireplace == "true", "flag_fireplace"] = 1
train[train$flag_tub == "", "flag_tub"] = 0
train[train$flag_tub == "true", "flag_tub"] = 1
train[train$tax_delinquency == "", "tax_delinquency"] = 0
train[train$tax_delinquency == "Y", "tax_delinquency"] = 1
# convert to date to int
train[,variable_date[variable_date %in% names(train)]] = 
  sapply(train[,variable_date[variable_date %in% names(train)]], as.character)
# convert to numeric to double
train[,variable_numeric[variable_numeric %in% names(train)]] = 
  sapply(train[,variable_numeric[variable_numeric %in% names(train)]], as.numeric)
# convert to discrete to int
combine_int_col = c(variable_discrete, variable_binary)
train[,combine_int_col[combine_int_col %in% names(train)]] = 
  sapply(train[,combine_int_col[combine_int_col %in% names(train)]], as.integer)
# convert to categorical to character
combine_char_col =  c(variable_nominal, variable_ordinal)
train[,combine_char_col[combine_char_col %in% names(train)]] = 
  sapply(train[,combine_char_col[combine_char_col %in% names(train)]], as.character)
```


```{eval = FALSE}
# 1. read/prepare data
################################################################################
setwd("D:/data_camp/zillow_project")
train <- read.csv('train_property.csv', stringsAsFactors = F)
train$trans_year <- sapply(strsplit(train$transactiondate, '-'), '[[', 1)
train$trans_month <- sapply(strsplit(train$transactiondate, '-'), '[[', 2)
train$trans_day <- sapply(strsplit(train$transactiondate, '-'), '[[', 3)
train$trans_weekday <- weekdays(as.Date(train$transactiondate))
train$trans_DATE <- as.Date(train$transactiondate)
# train rename
train <- plyr::rename(train,
                      c("parcelid"="id_parcel",
                        "transactiondate" = "trans_date",
                        "yearbuilt" = "build_year",
                        "basementsqft"="area_base_living",
                        "yardbuildingsqft17"="area_patio",
                        "yardbuildingsqft26"="area_shed",
                        "poolsizesum"="area_pool",
                        "lotsizesquarefeet"="area_lot",
                        "garagetotalsqft"="area_garage",
                        "finishedfloor1squarefeet" = "area_firstfloor_finished",
                        "calculatedfinishedsquarefeet" = "area_total_calc",
                        "finishedsquarefeet6" = "area_base",
                        "finishedsquarefeet12" = "area_live_finished",
                        "finishedsquarefeet13" = "area_liveperi_finished",
                        "finishedsquarefeet15" = "area_total_finished",
                        "finishedsquarefeet50" = "area_unknown",
                        "unitcnt" = "num_unit",
                        "numberofstories" = "num_story",
                        "roomcnt" = "num_room",
                        "bathroomcnt" = "num_bathroom",
                        "bedroomcnt" = "num_bedroom",
                        "calculatedbathnbr" = "num_bathroom_calc",
                        "fullbathcnt" = "num_bath",
                        "threequarterbathnbr" = "num_75_bath",
                        "fireplacecnt" = "num_fireplace",
                        "poolcnt" = "num_pool",
                        "garagecarcnt" = "num_garage",
                        "regionidcounty" = "region_county",
                        "regionidcity" = "region_city",
                        "regionidzip" = "region_zip",
                        "regionidneighborhood" = "region_neighbor",
                        "taxvaluedollarcnt" = "tax_total",
                        "structuretaxvaluedollarcnt" = "tax_building",
                        "landtaxvaluedollarcnt" = "tax_land",
                        "taxamount" = "tax_property",
                        "assessmentyear" = "tax_year",
                        "taxdelinquencyflag" = "tax_delinquency",
                        "taxdelinquencyyear" = "tax_delinquency_year",
                        "propertyzoningdesc" = "zoning_property",
                        "propertylandusetypeid" = "zoning_landuse",
                        "propertycountylandusecode" = "zoning_landuse_county",
                        "fireplaceflag" = "flag_fireplace",
                        "hashottuborspa" = "flag_tub",
                        "buildingqualitytypeid" = "quality",
                        "buildingclasstypeid" = "framing",
                        "typeconstructiontypeid" = "material",
                        "decktypeid" = "deck",
                        "storytypeid" = "story",
                        "heatingorsystemtypeid" = "heating",
                        "airconditioningtypeid" = "aircon",
                        "architecturalstyletypeid" = "architectural_style",
                        "pooltypeid10" = "flag_spa",
                        "pooltypeid2" = "flag_pool_spa",
                        "pooltypeid7" = "flag_pool_tub",
                        "fips"="county"))
# numerical variable
variable_numeric = c("area_firstfloor_finished",
                     "area_base", "area_base_living",
                     "area_garage", 
                     "area_live_finished",
                     "area_liveperi_finished",
                     "area_lot",
                     "area_patio",
                     "area_pool",
                     "area_shed",
                     "area_total_calc",
                     "area_total_finished",
                     "area_unknown",
                     "tax_building",
                     "tax_land",
                     "tax_property",
                     "tax_total",
                     "latitude",
                     "longitude")
# discrete
variable_discrete = c("num_75_bath",
                      "num_bath",
                      "num_bathroom",
                      "num_bathroom_calc",
                      "num_bedroom",
                      "num_fireplace",
                      "num_garage",
                      "num_pool",
                      "num_room",
                      "num_story",
                      "num_unit")
variable_binary = c("flag_fireplace",
                    "flag_tub",
                    "flag_spa",
                    "flag_pool_spa",
                    "flag_pool_tub",
                    "tax_delinquency")

# categorical variable
variable_nominal = c("aircon",
                     "architectural_style",
                     "county",
                     "deck",
                     "framing",
                     "heating",
                     "id_parcel",
                     "material",
                     "region_city",
                     "region_county",
                     "region_neighbor",
                     "region_zip",
                     "story",
                     "zoning_landuse",
                     "zoning_landuse_county")
variable_ordinal = c("quality")

# date
variable_date = c("tax_year",
                  "build_year",
                  "tax_delinquency_year",
                  "trans_year",
                  "trans_month",
                  "trans_day",
                  "trans_date",
                  "trans_weekday")

# others
variable_unstruct = c("zoning_property")

# don't understand
variable_unknown = c('censustractandblock',
                     'rawcensustractandblock')

# Conversion
# - convert some binary to 0, 1
# - convert to date to int
# - convert to numeric to double
# - convert to discrete to int
# - convert to categorical to character


train[train$flag_fireplace == "", "flag_fireplace"] = 0
train[train$flag_fireplace == "true", "flag_fireplace"] = 1
train[train$flag_tub == "", "flag_tub"] = 0
train[train$flag_tub == "true", "flag_tub"] = 1
train[train$tax_delinquency == "", "tax_delinquency"] = 0
train[train$tax_delinquency == "Y", "tax_delinquency"] = 1
# convert to date to int
train[,variable_date] = sapply(train[,variable_date], as.character)
# convert to numeric to double
train[,variable_numeric] = sapply(train[,variable_numeric], as.numeric)
# convert to discrete to int
train[,c(variable_discrete, variable_binary)] = sapply(train[,c(variable_discrete, variable_binary)], as.integer)
# convert to categorical to character
train[,c(variable_nominal, variable_ordinal)] = sapply(train[,c(variable_nominal, variable_ordinal)], as.character)

#drop  the redundant value
train <- train[, !(names(train) %in% c("num_bath","num_bathroom_calc","region_county","tax_year"))]

#deleting missing value
num.NA <- sort(colSums(sapply(train, is.na)))
remain.col <- names(num.NA)[which(num.NA <= 0.8 * dim(train)[1])] # 
train <- train[,remain.col]
####################################################################################

#2. missing value imputation
check.na <- function(train){
mis.col <- colSums(is.na(train))
mis.col <- mis.col[mis.col>0]
return(mis.col)
}

##(1) handle those have relative small missing value -> tax/total, tax_land/ tax_property
 
train[which(is.na(train$tax_total)),"tax_total"] <- train[which(is.na(train$tax_total)),"tax_property"]/
        quantile(train$tax_property/train$tax_total, 0.5, na.rm = T)

train[which(is.na(train$tax_property)),"tax_property"] <- train[which(is.na(train$tax_property)),"tax_total"]*
  quantile(train$tax_property/train$tax_total, 0.5, na.rm = T)

train[which(is.na(train$tax_land)),"tax_land"] <- train[which(is.na(train$tax_land)),"tax_total"]*
  quantile(train$tax_land/train$tax_total, 0.5, na.rm = T)

train[which(is.na(train$tax_building)),"tax_building"] <- train[which(is.na(train$tax_building)),"tax_total"]-
  train[which(is.na(train$tax_building)),"tax_land"]
check.na(train)

#2. then impute  region_zip/region_neighbor/region_city based on latitude/longtitude

#actually we might just delete region neighbor, because  the missing value does  not contain 
#any information, and we have  to bother to impute it

with(train,t.test(logerror~ is.na(region_neighbor)))

# p-value is 0.07, we  can accept the  null hypothesis, region_neighbor does not contain info
#for those who are interested, take a look at how to find the nearest datapoint
#https://stackoverflow.com/questions/21977720/r-finding-closest-neighboring-point-and-number-of-neighbors-within-a-given-rad

geo.df <- train[,c("latitude","longitude","region_zip","region_city")]

library(sp)
library(rgeos)

Impute.Zip<- function(row,search.range=1000){
    geo.df.trunc <-subset(geo.df, abs(geo.df$longitude + geo.df$latitude -
                                                          unlist(row["longitude"])-unlist(row["latitude"]))<search.range)
    
    coordinates(geo.df.trunc) <- ~longitude+latitude
    d <- gDistance(geo.df.trunc, byid=T)
    k = 2
    min.d <- apply(d, 1, function(x) order(x, decreasing=F)[k])
    neighbor <- min.d[rownames(row)]
    while(is.na(geo.df.trunc[neighbor,"region_zip"]$region_zip)){
      k = k + 1
      min.d <- apply(d, 1, function(x) order(x, decreasing=F)[k])
      neighbor <- min.d[rownames(row)]
      
    }
    return(geo.df.trunc[neighbor,"region_zip"]$region_zip)
}

na.zip.rowname <- which(is.na(train$region_zip))

for (i in na.zip.rowname){
  row <-  geo.df[i,]
  geo.df[i,"region_zip"] = Impute.Zip(row)
}

#similarly, impute city

Impute.city<- function(row,search.range=1000){
  geo.df.trunc <-subset(geo.df, abs(geo.df$longitude + geo.df$latitude -
                                      unlist(row["longitude"])-unlist(row["latitude"]))<search.range)
  
  coordinates(geo.df.trunc) <- ~longitude+latitude
  d <- gDistance(geo.df.trunc, byid=T)
  k = 2
  min.d <- apply(d, 1, function(x) order(x, decreasing=F)[k])
  neighbor <- min.d[rownames(row)]
  while(is.na(geo.df.trunc[neighbor,"region_city"]$region_city)){
    k = k + 1
    min.d <- apply(d, 1, function(x) order(x, decreasing=F)[k])
    neighbor <- min.d[rownames(row)]
    
  }
  return(geo.df.trunc[neighbor,"region_city"]$region_city)
}

na.city.rowname <- which(is.na(train$region_city))

count = 0

for (i in na.city.rowname){
  count = count + 1
  print(count)
  print(i)
  row <-  geo.df[i,]
  geo.df[i,"region_city"] = Impute.city(row)
}


train[,c("region_zip","region_city")] = geo.df[,c("region_zip","region_city")]
train <- train[,!names(train) != "region_neighbor"]

#delete censustractandblock, region_neighbor -> do not have explain power

train <- train[,!names(train) %in%c("X.1","X","censustractandblock","region_neighbor")]
check.na(train)
names(train)
plot(train$area_lot,train$area_lot)

#reduandant variable, delete area_live_finished
train <- train[,!names(train) == "area_live_finished"]

#fisrt handle  some simple one, we create a new level to indicate missing value

train$aircon <- ifelse(is.na(train$aircon),"missing",train$aircon)
train$num_garage <- ifelse(is.na(train$num_garage),"missing",train$num_garage)
train$area_garage <- ifelse(is.na(train$area_garage),"missing",train$area_garage)
train$heating<- ifelse(is.na(train$heating),"missing",train$heating)
train$num_story<- ifelse(is.na(train$num_story),"missing",train$num_story)
train$quality<- ifelse(is.na(train$quality),"missing",train$quality)
train$build_year<- ifelse(is.na(train$build_year),"missing",train$build_year)
check.na(train)

# then let us impute the remaining missing value using library(mice)
# we have aleady got number infomation, for now, I did not see the explanation power in num_unit

train <- train[,!names(train) == "num_unit"]
library("mice")

#put all the columns related to area

area.col <- c("area_lot","area_total_calc","num_bedroom","num_bathroom","num_room","tax_total")
imputed_Data <- mice(train[,area.col], m=1, maxit = 10, method = 'pmm', seed = 500)
plot(train$area_lot,complete(imputed_Data,1)$area_lot)
train$area_lot = complete(imputed_Data,1)$area_lot
abline(0,1)

train$area_total_calc = complete(imputed_Data,1)$area_total_calc

#check missing value
check.na(train)

# here, numerical value can't contain NA
plot(table(train$num_garage))

#keep one, delete  garage_area
train <- train[,!names(train) == "area_garage"]

#delete num_story
with(train, t.test(logerror~ is.na(num_story)))
train <- train[,!names(train) == "num_story"]
with(train, t.test(logerror~ is.na(num_garage)))
train <- train[,!names(train) == "num_garage"]

```

##2 Feature  Engineering

We seperate all the  features into  several different categories, then perform the feature engineering within categories. Here is a summary of feature engineering.

####(1) Date-realted features

(a) "weekend": whether the sold day is weekend

(b) "Q2": whether the sold day belongs to Q2

(c) "ancient level": categorize built year by cut (1940, 1995)

The above  three features cover up day - week - season -year.

Note: the reasons I came up with the coming three features is due to visualization result by plotting mean(error)~ category.

```{r,warning=FALSE,message=FALSE}
variable_date = c("build_year",
                  "trans_year",
                  "trans_month",
                  "trans_day",
                  "trans_date",
                  "trans_weekday")


# trans_weekday
par(mfrow = c(1,1))
boxplot(subset(train,trans_weekday == "Monday" &
          abs(logerror)<0.145)$logerror,
        subset(train,trans_weekday == "Tuesday" &
                 abs(logerror)<0.145)$logerror,
        subset(train,trans_weekday == "Wednesday" &
                 abs(logerror)<0.145)$logerror,
        subset(train,trans_weekday == "Thursday" &
                 abs(logerror)<0.145)$logerror,
        subset(train,trans_weekday == "Friday" &
                 abs(logerror)<0.145)$logerror,
        subset(train,trans_weekday == "Saturday" &
                 abs(logerror)<0.145)$logerror,
        subset(train,trans_weekday == "Sunday" &
                 abs(logerror)<0.145)$logerror
        )
with(train,t.test(logerror~ trans_weekday == "Saturday"|trans_weekday == "Sunday"))

#new feature 1.
train$weekend =ifelse(train$trans_weekday== "Saturday"|train$trans_weekday == "Sunday",
                       1,0)

train$ancient.level <- ifelse(train$build_year == "missing","missing",
                              ifelse(as.integer(train$build_year)>1995,"new",
                                ifelse(as.integer(train$build_year)>1940,"old","ancient")))

train$Q2 = with(train,ifelse(trans_month %in% c("4","5","6"),"1","0"))
date.feature <- c("weekend","Q2","ancient.level")

```


####(2) room/area related features
```{r,warning=FALSE,message=FALSE}

plot(train$num_room,  train$num_bedroom + train$num_bathroom)

with(train,t.test(abs(logerror)~ num_room >= num_bedroom + num_bathroom))

#whether the number of room is larger than the sum of the number of bedroom/bathroom

train$right_room <- with(train,ifelse(num_room >= num_bedroom + num_bathroom,1,0))

# bedroom/ bathroom ratio
train$bed_to_bath <- with(train,ifelse(num_bathroom == 0, 0,num_bedroom/num_bathroom))

#examine the correlation to see whether the  the features are informative features
cor(train$bed_to_bath,train$logerror)
cor(train$bed_to_bath,abs(train$logerror))
cor(train$num_bathroom,abs(train$logerror))

#Generate  other features 

train$are_per_room<- with(train,ifelse(num_room == 0, 0, area_total_calc/num_room))

#dummy variable indicating whether the count of room is zero
train$zero_room <- with(train, ifelse(num_room  ==0 ,1,0))

cor(train$are_per_room,abs(train$logerror))
cor(train$area_total_calc,abs(train$logerror))

par(mfrow = c(1,1))

with(train,plot(area_lot),plot(area_total_calc))

room.area.feature <- c("num_room","num_bedroom","num_bathroom","right_room","bed_to_bath",
                       "are_per_room","zero_room","area_total_calc")


```


###(3) facility realted features
```{r,warning=FALSE,message=FALSE}
table(train$aircon)
by(train,train$aircon,function(x){mean(x$logerror)})

#collapse categorical features with too many levels
#rebuild level based on mean  log_error
train$new.aircon = with(train,ifelse(aircon=="missing",aircon,
                                ifelse(aircon=="5"|aircon=="13","5/13",
                                  ifelse(aircon=="11","11","1/3/9"))))

table(train$heating)

by(train,train$heating,function(x){mean(x$logerror)})

# capllase heating's level to new heating
train$new.heating = with(train,ifelse(heating == "missing",heating,
                                  ifelse(heating %in% c("10","11","12","13","14","20","24"),"neg",
                                         ifelse(heating %in% c("6","7"),"6/7","2/1/18"))))

#Create new level to indicate whether the categorical variavle is missing
train$missing.heating <- with(train,ifelse(heating == "missing",1,0))
train$missing.aircon <- with(train,ifelse(aircon == "missing",1,0))

facility.feature <- c("flag_tub","flag_fireplace","missing.aircon","new.heating")


```

###(4) tax realted features
```{r,warning=FALSE,message=FALSE}

with(train,cor(tax_delinquency,logerror))

# Create tax percentage indicating the percentage of tax paid  
train$tax.perc <- train$tax_property/ train$tax_total
with(train,cor(tax.perc,logerror)) 
train$right.tax <-ifelse(train$tax.perc < 0.1,1,0)
train$build.to.total <- train$tax_building/train$tax_total
with(train,cor(build.to.total,logerror)) 
train$tax.per.area <-  train$tax_property/train$area_total_calc
tax.feature <- c("tax_delinquency","tax_total","tax_property","tax_land","right.tax","tax.per.area","build.to.total","tax.perc")

```

###(5)Overall  evaluation  feature(Collapse quality )
```{r,warning=FALSE,message=FALSE}
quality.error <- by(train,train$quality, function(x){mean(x$logerror)})
table(train$quality) 

#collapse quality features based on their  influence  on response
train$new.quality <- with(train,ifelse(quality=="missing",quality,
                                ifelse(quality %in% c("12","7","11"),"12-7-11",
                                ifelse(quality %in% c("4","1"), "4-1","6-8-10")
                                       )
  
))

quality.feature <- c("new.quality")

```

###(6) geometry related feature 
```{r,warning=FALSE,message=FALSE}

zip.num <- by(train, train$region_zip, function(x) nrow(x))
train$zip.num <- zip.num[train$region_zip]

zip.area  <- by(train, train$region_zip, function(x) 
{abs((max(x$longitude) - min(x$longitude))*(max(x$latitude) - min(x$latitude)))})
train$zip.area <- zip.area[train$region_zip]

zip.density <- ifelse(zip.area  == 0 , 0 ,zip.num/zip.area)
zip.density.accuracy <- ifelse(zip.num>50,1,0)
zip.density.revised  <- zip.density*zip.density.accuracy
train$zip.density.revised <- zip.density.revised[train$region_zip]

plot(density(zip.density))
plot(zip.density)
train$zip.density <- zip.density[train$region_zip]
with(train,cor(zip.density,logerror))
with(train,cor(zip.density,abs(logerror)))
train$zip.density <- zip.density[train$region_zip]

##
city.zip <- by(train,train$region_city, function(x){length(unique(x$region_zip))})
train$zip.per.city <- city.zip[train$region_city]
with(train,cor(zip.per.city ,logerror))

city.area <- by(train, train$region_city, function(x){abs((max(x$longitude) - min(x$longitude))*(max(x$latitude) - min(x$latitude)))})

city.num  <- by(train, train$region_city, function(x) nrow(x))
city.density <- city.area/city.num
train$city.density <- city.density[train$region_city]
with(train,cor(city.density ,abs(logerror)))
train$county6111 <- with(train, ifelse(county == "6111",1,0))
####SELECT features 
geo.feature<- c("county6111","zip.density.revised")

```

## build linear model

Here, we do not list every linear model built. Instead, we just give an example to show the basic idea of how to transform features using residual diagnosis.

```{r,warning=FALSE,message=FALSE}
selected.feature <- c("logerror",geo.feature,quality.feature,tax.feature,facility.feature,room.area.feature,date.feature)
reg.df <- train[,selected.feature]

full.model <- lm(logerror~.,data = reg.df)
summary(full.model)

```

Then let us start the model selection using lasso regression.
```{r,warning=FALSE,message=FALSE}
library(glmnet)
ind = model.matrix(~.,reg.df[,-1])
dep = reg.df$logerror
fit <- glmnet(x=ind, y=dep)
plot(fit, xvar = "lambda", label = T)

cvfit <- cv.glmnet(ind, dep)
cvfit$lambda.min 
plot(cvfit)

x = coef(cvfit, s = "lambda.min")
x

```

We can  see lasso regression did not really help us choose some features. 

However, we want to use residual plot to seek for new opportunies to improve the mdoel. I will just give an example for the feature bedroom to bathroom rate.

After  performing the square root transfromation, the residual plot will look better. And we trained the model agian,  the adjusted R-square does improve as well.

Then, for each feature, we tried to perform the some transformation, also include  some  intersection terms. 

After trying different transformations  and intersactions, I showed the best result bewlow.

```{r,warning=FALSE,message=FALSE}
mod <- lm(logerror~.-zip.density.revised +I((train$zip.density.revised)^(1/18))
           -are_per_room + I(are_per_room^(1/15))
           -county6111-new.quality
           #-tax_land +I(tax_land^(1/2))
           -tax_property + I(tax_property^(1/60))
           -num_room 
           -bed_to_bath + I((bed_to_bath)^(1/2))
           -tax.per.area + I(tax.per.area^(1/50))
           -flag_fireplace
           -missing.aircon 
           -tax.perc + I(tax.perc^(1/12))
           -right.tax  
           + right.tax:I(tax_land^(1/3))
           +I(build.to.total^(1/60))
          + flag_tub : new.heating
          +right_room : zero_room
          -flag_tub
          +Q2:weekend

           ,data = reg.df)
summary(mod)

```
