---
title: "Zillow_EDA"
author: "Yue Wen"
output: pdf_document
---
This RMD file is the inital explotory data analysis of zillow data set.
```{r,message=FALSE, warning=FALSE}
# install necessary library
library(tabplot)
library(lattice)
setwd("D:/data_camp/zillow_project")
train <- read.csv("train_property.csv",stringsAsFactors = FALSE)
```
# 1. Data cleaning
We noticed that there are some missing values, let us examine the missing value first.
```{r,message=FALSE, warning=FALSE}
#check the number of missing values in each column
num.NA  <- sort(colSums(sapply(train,is.na)))
num.NA.perc <- num.NA/dim(train)[1]
```
We can see a lot features have a large portion of missing value. However, before we decided
to delete some of these features, let us take a look at whether the missing proportion of each row might  influence the respond variable. The purpose of doing so is to make sure thatthe percentage of missing value in each row do not have influence on logerror.

```{r,message=FALSE, warning=FALSE}
row.NA.perc <- rowSums(sapply(train,is.na))/dim(train)[2]
log.error <- train$logerror
cor(log.error,row.NA.perc)
```
We can see the  corrlation is all most 0. So for now, let us delete these features that
has  more than 80% missing value

```{r,message=FALSE, warning=FALSE}
#  if more than 80% of feature is missing, then we delete the feature.
delete.thredshold <- 0.2
remain.rows <- names(num.NA)[num.NA.perc < delete.thredshold]
train <- train[ , remain.rows]
print(paste(ncol(train)/ncol(train),"of the features are not deleted"))
```
Done!  We cleaned up the  NA part for now.

The other thing we  have to do is to set some of the feature to character for further exploration
```{r,message=FALSE, warning=FALSE}
train[, c('fips', 'propertylandusetypeid', 'rawcensustractandblock', 'regionidcounty', 'assessmentyear', 'regionidzip', 'censustractandblock', 'regionidcity')] <-
  as.character(train[, c('fips', 'propertylandusetypeid', 'rawcensustractandblock', 'regionidcounty', 'assessmentyear', 'regionidzip', 'censustractandblock', 'regionidcity')])
```

# 2. EDA
First let us take  a look at the distribution of logerror
```{r,message=FALSE, warning=FALSE}
plot(density(train$logerror))
boxplot(train$logerror)
```
Just get a basic idea of the whole data set, we can see it is pretty centered at zero. 

Then, one natural thing to do is to look at the correlation ofdifferent numeric features.
#correlation -> use more in   continuous variable
```{r,message=FALSE, warning=FALSE}
library(corrplot)
correlations <- cor(train[, c('logerror', 'bathroomcnt', 'bedroomcnt', 'roomcnt',
                              'taxamount', 'calculatedfinishedsquarefeet',
                              'calculatedbathnbr', 'fullbathcnt', 'finishedsquarefeet12', 'lotsizesquarefeet')], 
                    use = "pairwise.complete.obs")

corrplot(correlations, method = "square", tl.cex = 1, type = 'upper')
```
We can see the value in coraltion matrix are very small, which only means there are not linear relationship, but there might be other relationships. We still cannot draw any conclusion too easily.

Then let us take a look at the  relationships between different features and response variable.

## 1. transaction month
```{r,message=FALSE, warning=FALSE}
#extract transaction month from date data
train$txnmonth <- sapply(strsplit(train$transactiondate, '-'), 
                         function(x) x[2])

err.month <- by(train,train$txnmonth,function(x) mean(x$logerror))

plot(names(err.month),err.month,type = "l")
```
The mean value is relatively low from March to August, there are definitely information here which might help us predict logerror in the future. 
##2. built year
```{r,message=FALSE, warning=FALSE}

tableplot(train, select = c('logerror', 'yearbuilt'),sortCol = "yearbuilt")

bwplot(logerror ~ yearbuilt, data = train)

err.yearbuilt <- by(subset(train,train$logerror<0.9), subset(train,train$logerror<0.9)$yearbuil, function(x) mean(x$logerror))

plot(names(err.yearbuilt), err.yearbuilt,type = "l")
```
Built year does not seem to influence the response variable.


##3. bedroom 
```{r,message=FALSE, warning=FALSE}
err.bedroomcnt <- by(train, train$bedroomcnt, function(x) mean(x$logerror))
plot(names(err.bedroomcnt), err.bedroomcnt,type = "l")
```
It  seems like it declines a little bit when the bedroom number gets larger.
##4. bathroom 
```{r,message=FALSE, warning=FALSE}
err.bathroomcnt <- by(train, train$bathroomcnt, function(x) mean(x$logerror))
plot(names(err.bathroomcnt), err.bathroomcnt,type = "l")
```
The trend is prettly similar with the that of the bathroom.
##5. roomcnt
```{r,message=FALSE, warning=FALSE}
tableplot(train, select = c('logerror', 'roomcnt'),sortCol = "roomcnt")
bwplot(logerror ~ roomcnt, data = train)
err.roomcnt <- by(subset(train,train$logerror<0.9), 
                  subset(train,train$logerror<0.9)$roomcnt,
                  function(x) mean(x$logerror))
plot(names(err.roomcnt), err.roomcnt,type = "l")
```
This feature influences the mean logerror as well, we can see point 2 minimizes the mean logerror.
##6.finishedsquarefeet12
```{r,message=FALSE, warning=FALSE}
err.finishedsquarefeet12 <- by(subset(train,train$logerror<0.9), 
                  subset(train,train$logerror<0.9)$finishedsquarefeet12,
                  function(x) mean(x$logerror))

plot(names(err.finishedsquarefeet12), err.finishedsquarefeet12,type = "l")
```
Look like a siginal,  however, it can just be noise. I don't think this can be a good predictor.

##7. taxamont
```{r,message=FALSE, warning=FALSE}
err.taxamount <- by(subset(train,train$logerror<0.9), 
                  subset(train,train$logerror<0.9)$taxamount,
                  function(x) mean(x$logerror))
plot(names(err.taxamount), err.taxamount,type = "l")
```
The same conclusion as the previous one.
##8.fips
```{r,message=FALSE, warning=FALSE}
err.fips <- by(subset(train,train$logerror<0.9), 
                    subset(train,train$logerror<0.9)$fips,
                    function(x) mean(x$logerror))
plot(density(err.fips))
```
We can see the densitly is like a normal distribution. So fips does influence logerror.

##9.regionidzip
```{r,message=FALSE, warning=FALSE}
err.regionidzip <- by(subset(train,train$logerror<0.9), 
               subset(train,train$logerror<0.9)$regionidzip,
               function(x) mean(x$logerror))
plot(density(err.regionidzip))
```
The same as the previous one, they are all considered as region factors.

##10.has hot tub or spa
```{r,message=FALSE, warning=FALSE}
bwplot(logerror~hashottuborspa, data = subset(train,train$logerror < 0.9))
```
I thought this one might influence the result, however, it  seems like it does not.

Except those feature, we create some new features.

#new features 
##1. bedroom  to bathroom count
```{r,message=FALSE, warning=FALSE}
train$bedrm.to.bathrm <- train$bedroomcnt/train$bathroomcnt

train.trunc <- subset(train,!is.na(train$bedrm.to.bathrm))
plot(train.trunc$bedrm.to.bathrm, train.trunc$logerror)
```
We can see that When the ratio is low, it seems logerror is  bigger.


##2. seasonality
```{r,message=FALSE, warning=FALSE}
season <- function(num){
  num <- as.integer(num)
  ifelse(num %in% c(1,2,12),"winter",
                  ifelse(num %in% c(3,4,5),"spring",
                          ifelse(num %in% c(6,7,8),"summer","autumn")))
}
train$season <- sapply(train$txnmonth, season)
bwplot(logerror~season,data=subset(train,train$logerror < 0.9))
```
It seems like  it does not differ too much  from season  to  season

# Next steps:
keep exploring what other features can  be and take a deeper look at current features.